Meta-analysis

### 2019-11-01 05_MetaAnalysis.Rmd
spell check

```{r row_spacing.m}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole" | fungicide_ai == "propiconazole") %>%
   group_by(fungicide_ai, row_spacing, trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Trials = n) %>%
   ggplot(aes(x = as.factor(row_spacing), y = Trials)) +
   xlab("Row Spacing (m)") +
   ylab("N Trials") +
   ggtitle(label = "Trial row spacings using tebuconazole") +
   geom_col(aes(fill = fungicide_ai),
            position = "dodge") +
   scale_fill_usq(name = "Fungicide AI") +
   theme_usq()

@@

Were there any statistical difference between all row spacing or only some?
Can we pool certain row spacings that have no significant difference?
From the preliminary analysis, the graphs seem to imply that if there is a lower overall yield there is no effect of row spacing on yield.
However, if the average yield is more than approximately 0.6 - 1 t/ha then smaller row spacing has the potential to provide greater yield.

@@

The approximate period when in-crop rainfall impacts the most on the mean harvest is bettween 11 - 88 days after planting.

@@

### Converting least-squares tp sample variance

>>>>

```{r row_spacing.m}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole" | fungicide_ai == "propiconazole") %>%
   group_by(fungicide_ai, row_spacing, trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Trials = n) %>%
   ggplot(aes(x = as.factor(row_spacing), y = Trials)) +
   xlab("Row Spacing (m)") +
   ylab("N Trials") +
   ggtitle(label = "Trial row spacing using tebuconazole") +
   geom_col(aes(fill = fungicide_ai),
            position = "dodge") +
   scale_fill_usq(name = "Fungicide AI") +
   theme_usq()

@@

Were there any statistical difference between all row spacing or only some?
Can we pool certain row spacing that have no significant difference?
From the preliminary analysis, the graphs seem to imply that if there is a lower overall yield there is no effect of row spacing on yield.
However, if the average yield is more than approximately 0.6 - 1 t/ha then smaller row spacing has the potential to provide greater yield.

@@

The approximate period when in-crop rainfall impacts the most on the mean harvest is between 11 - 88 days after planting.

@@

### Converting least-squares to sample variance
